---
title: "Datathon 2021"
author: "Khushmeet Chandi, Athena Ru, Jason Ren"
date: "November 6, 2021"
output: pdf_document
---
```{r packages, include=FALSE}
#library(inspectdf)
library(foreign)
library(tidyverse)
library(dplyr)
library(haven)
library(tidymodels)
```
```

```{r reading-thailand-data}
thailand <- read_sav("data/W1 Merged Data/Wave.1_Data/Thailand/Thailand v4.2.sav")
thailand
```

```{r public-water-supply-data-thailand}
thailand <- thailand %>%
  drop_na(ir010b) %>%
  filter(ir010b!=99)
  
ggplot(thailand, mapping=aes(ir010b)) +
  geom_bar() +
  labs(
    title = "How do interviewees rate the sanitary condition in the public area
            in their nearby neighborhood?",
    x="Rating of the Sanitary Condition in the Public Area",
    y="Frequency"
  )
```

This dataset includes 1539 rows with 259 columns. This indicates that there were
1539 survey respondents and 259 pieces of information collected from these
respondents. The particular data that we are interested in in this study is the
santiary conditions in the interviewees' nearby neighborhood. This data is 
categorical. The santiary conditions will be compared to the avalaibiity of
clean drinking water and electricity to determine the economic and public health
conditions in the countries provided in the dataset. This will then be 
analyzed and compared against the percieved economic condition in those countries,
using the respondents' rating of how they view the economic condition in their
country. In summary, this will provide insight into how the economic conditions
of Asian countries compare to one another and how the countries' residents
percieve these economic conditions. 
